The Ranked Nearest Neighbour Interchange space

### 2019-06-11 paper.tex
connection alg:find_path and alg:max_dist_tree

The proof of Theorem 7 in \cite{Gavryushkin2017} gives an algorithm to compute paths between trees in $\rnni$.

@@

\begin{corollary}
It is $\Delta(\rnniu) = \frac{1}{2}n^2-\frac{3}{2}n+1$.
\end{corollary}

@@

\begin{algorithm}[H]
\caption{MAX\_DISTANCE\_TREE($T$)}
\label{alg:max_dist_tree}
\begin{algorithmic}[1]
	\STATE $R$ only contains cherry taxa of $T$ and has internal node with rank $n-1$
    \STATE In list $L$ all taxa $\{1,\ldots,n\}$ are sorted such that the ranks of their parents in $T$ do not decrease
	\FOR {taxon $a$ in $L$}
		\STATE Add an internal node as parent of $a$ on any edge in $R$ such that the new internal node has rank one less than the previously lowest internal node
	\ENDFOR
	\RETURN $R$
\end{algorithmic}
\end{algorithm}

>>>>

The proof of Theorem 7 in \cite{Gavryushkin2017} gives an algorithm to compute paths between trees in $\rnni$. %Do we want to mention that algorithm here?

@@

\begin{corollary}
It is $\Delta(\rnniu) = \frac{(n-1)(n-2)}{2} = \frac{1}{2}n^2-\frac{3}{2}n+1$.
\end{corollary}

@@

\begin{algorithm}[H]
\caption{MAX\_DISTANCE\_TREE($T$)}
\label{alg:max_dist_tree}
\begin{algorithmic}[1]
	\STATE $R$ only contains cherry taxa $(a,b)$ of $T$ and has internal node with rank $n-1$
    \STATE In list $L$ all taxa $\{1,\ldots,n\}\setminus\{a,b\}$ are sorted such that the ranks of their parents in $T$ do not decrease
	\FOR {taxon $a$ in $L$}
		\STATE Add an internal node as parent of $a$ on any edge in $R$ such that the new internal node has rank one less than the previously lowest internal node
	\ENDFOR
	\RETURN $R$
\end{algorithmic}
\end{algorithm}

\begin{lemma}
    Let $T$ and $R$ be trees.
    Algorithm~\ref{alg:find_path} gives a path of length $\frac{(n-1)(n-2)}{2}$ between $T$ and $R$ if, and only if, $R$ can be generated from $T$ by applying Algorithm~\ref{alg:max_dist_tree}.
\end{lemma}
